---
title: "Week1 Notes"
output: html_notebook
---
What a Code Book should contain
1) information about variables
    in the data set not contained in the tidy data
2) Information about the summary choices made
3) Information about the experimental study design used

A common format: Word/text file
There should be a section called "Study Design" that has a through description of how you collected data.

The instruction list
- Ideally in R script
- The input is raw data
- The output is the processed, tidy data
- There are no parameters to the script


Get/set working directory
-In Mac OS: 
```{r}
setwd("./data")
```

-In Windows 
```{r}
setwd("C:\\Users\\Andrew\\Downloads")
```

Checking for and creating directories
```{r}
if (!file.exists("data")){
    dir.create("data")
}
```

Getting data from the Internet
```{r}
download.file(url = , destfile = , )
```

An example of downloading datat form baltimorecity website
```{r}
fileUrl <- "https://data.baltimorecity.gov/api/views/dz54-2aru/rows.csv?accessType=DOWNLOAD"
download.file(fileUrl, destfile = "./data/cameras.csv", method = "curl") #we only need to set the method to curl in MAC, while in Windows the HTTPS are the default method
# It doesn't work because the url does not work!
list.files("./data")
dateDownloaded <- date()
```


How to open local file
- I downloaded the Baltimore fixed camera dataset mannually and save it in the file in "./data/Fixed_Speed_Cameras.csv"

Now try to read it!
```{r}
cameraData <- read.csv("./data/Fixed_Speed_Cameras.csv")
head(cameraData)
```
Some important parameters
quote - sometimes we should set quoted=""
na.strings - set the character that repressent a missing value
nrows - how many rows to read
skip - number of lines to skip befere starting to read


read Excel files
```{r}
library(xlsx)
camrraData2 <- read.xlsx("./data/xxx.xlsx",sheetIndex = 1, header = TRUE)
```
- read.xlxs2 is much faster than read.xlsx but for reading subsets of rows may be slightly unstable

- XLConnect package has more options for writing and manipulating Excel files
- XLCnonnect cignette is a good place to start for that package



Reading XML

1)Tags, elements and attributes
  Tages - Start tages <section>
        - End tages </section>
        - Empty tags<line-break />
  Elements
        - <Greeting> Hello, world </Greeting>
  Attributes are componets of the label
        - <img scr = "jeff.jpg"> alt="instructor"/>
        - <step number ="3"> Connect A to B. </step>
        
```{r}
library(XML)
fileUrl <- "http://www.w3schools.com/xml/simple/xml"
doc <-xmlTreeParse(fileUrl, useInternalNodes = TRUE)
rootNode <- xmlRoot(doc)

#Progarammatically extract parts of the file
xmlSApply(rootNode, xmlValue)
```
Get the items on the menu and prices
```{r}
xpathApply(rootNode"//name",xmlValue)
xpathApply(rootNode"//price",xmlValue)
```


```{r}
myUrl <- "https://www.espn.com/nfl/team/_/name/bal/baltimore-ravens"
doc <- htmlTreeParse(myUrl, useInternal = TRUE)
scores <- xpathSApply(doc, "//li[@class='score']",xmlValue)
teams <- xpathSApply(doc, "//li[@class='team-name']",xmlValue)
```


Reading Javascript Object Notation(JSON)
- Lightweight data storage
```{r}
library(jsonlite)
jsonDATA <- fromJSON("https://api.github.com/users/Zixuan-YU/repos")
#names(jsonDATA)
names(jsonDATA$owner)
jsonDATA$owner$login
```
Writing data frames to JSON
```{r}
myjson <- toJSON(iris, pretty = TRUE)
cat(myjson)
```

Convert back to JSON
```{r}
iris2 <- fromJSON(myjson)
head(iris2)
```

More informations about JSON:
1) http://www.json.org/
2) tutorail: http://www.r-bloggers.com/new-package-jsonlite-a-smarter-json-encoderdecoder/
3) jsonlite vignette





Data.table 
1) written in C and much faster
2) all functions accept data.frame work on data.table
```{r}
library(data.table)
DT = data.table(x=rnorm(9), y=rep(c("a","b","c"),each=3), z=rnorm(9))
head(DT,3)
```
```{r}
tables()
```
#see all the data tables in memory

subsetting rows
```{r}
DT[2,]
```
subsetting rows
```{r}
DT[c(2,3)]
#如果不加逗号，就是subsetting based on rows
#此处需要注意！与data frame不同
```
subsetting columns!! DIFFERENT
```{r}
{
  x = 1
  y = 2
}
k = {print(10); 5}
```
```{r}
print(k)
```

Calculating values for variables with expressions
```{r}
DT <- data.table(x=rnorm(9), y=rep(c("a","b","c"),each=3), z = rnorm(9))
DT
DT[,list(mean(x),sum(z))]
DT[,table(y)]
```
Adding new columns, using ":="
```{r}
DT
DT[,w:=z^2]
```
```{r}
DT2 <- DT
```

Multiple operations
```{r}
DT[,m:={tmp <-(x+z); log2(tmp+5)}]
```

plyr like operations
```{r}
DT[,a:=x>0]
DT[,b:=mean(x+w),by=a]
```


Sepcial Variables
.N An integer, lenth 1, containing the number
```{r}
set.seed(123);
DT <- data.table(x=sample(letters[1:3],1E5,TRUE))
DT[, .N, by=x]
```


Keys
```{r}
DT <- data.table(x=rep(c("a","b","c"),each=100), y=rnorm(300))
setkey(DT, x)
DT['a']
```

Joins
```{r}
DT1 <- data.table(x=c("a","a","b","dt1"),y=1:4)
DT2 <- data.table(x=c("a","b","dt2"),z=5:7)
setkey(DT1, x)
setkey(DT2, x)
merge(DT1,DT2)
```
Fast Reading
```{r}
big_df <- data.frame(x= rnorm(1E6), y=rnorm(1E6))
file <- tempfile()
write.table(big_df, file = file, row.names = FALSE, col.names = FALSE, sep = "\t", quote = FALSE)
system.time(fread(file))
```
```{r}
system.time(read.table(file, header = TRUE, sep = "\t"))
```


the differences with df and dt: https://stackoverflow.com/questions/13618488/what-you-can-do-with-a-data-frame-that-you-cant-with-a-data-table


When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

