---
title: "EDA_week1_project1_power_consumption"
author: "Zixuan Yu"
date: "7/2/2022"
output: md_document
---
When loading the dataset into R, please consider the following:

- The dataset has 2,075,259 rows and 9 columns. First calculate a rough estimate of how much memory the dataset will require in memory before reading into R. Make sure your computer has enough memory (most modern computers should be fine).

- We will only be using data from the dates 2007-02-01 and 2007-02-02. One alternative is to read the data from just those dates rather than reading in the entire dataset and subsetting to those dates.

- You may find it useful to convert the Date and Time variables to Date/Time classes in R using the \color{red}{\verb|strptime()|}strptime()  and \color{red}{\verb|as.Date()|}as.Date() functions.

- Note that in this dataset missing values are coded as \color{red}{\verb|?|}?.

```{r}
power <- read.table('C:/REPO/datasciencecoursera/4.Exploratory_Data_Analysis/exdata_data_household_power_consumption/household_power_consumption.txt', sep = ";", header = T,na.strings="?",colClasses = c(character(),
                                         character(),
                                         numeric(),
                                         numeric(),
                                         numeric(),
                                         numeric(),
                                         numeric(),
                                         numeric(),
                                         numeric()))
str(power)
```
```{r}
library(lubridate)
library(dplyr)

power <- power %>% mutate(exact_time = paste(Date, Time, sep=" "))
head(power$exact_time)
```

```{r}
library(dplyr)
library(tidyverse)
power$exact_time2 <- lubridate::dmy_hms(power$exact_time)
power$datee <- dmy(power$Date)
#dat <- power %>% filter(lubridate::date(exact_time2) %in% c(as.Date("2007-02-01"),as.Date("2007-02-02")))
dat <- power %>% filter((datee >= "2007-02-01") & (datee <= "2007-02-02"))
head(dat)
```


```{r Plot1}
#png("plot1.png")
#dat$Global_active_power <- as.numeric(dat$Global_active_power)
hist(as.numeric(dat$Global_active_power),
     main = "Global Active Power",
     xlab = "Global Active Power (kilowatts)",
     xlim = c(0,6),
     col = "red")
#dev.off()
# breaks = c(0.0, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0),
```


```{r Plot2}
#png("plot2.png")
    plot(dat$exact_time2,
         dat$Global_active_power,
         type="l",
         xlab="",
         ylab="Global Active Power (kW)")
#dev.off()
```

```{r Plot3}
#png("plot3.png")
    plot(dat$exact_time2,
         dat$Sub_metering_1,
         type="l",
         xlab="",
         ylab="Energy sub metering")
    lines(dat$exact_time2,
         dat$Sub_metering_2,
         type="l",
         col = "red")
    lines(dat$exact_time2,
         dat$Sub_metering_3,
         type="l",
         col = "blue")
    legend(x = "topright",
           legend = c("Sub_metering_1","Sub_metering_2","Sub_metering_3"),
           lty = 1,
           lwd = 2.5,
           col = c("black","red","blue"))
#dev.off()
```
```{r Plot4}
#png("plot4.png")

par(mfrow = c(2,2))
    plot(dat$exact_time2,
         dat$Global_active_power,
         type="l",
         xlab="",
         ylab="Global Active Power (kW)")

    plot(dat$exact_time2,
         dat$Voltage,
         type="l",
         xlab="datetime",
         ylab="Voltage")

    plot(dat$exact_time2,
         dat$Sub_metering_1,
         type="l",
         xlab="",
         ylab="Energy sub metering")
    lines(dat$exact_time2,
         dat$Sub_metering_2,
         type="l",
         col = "red")
    lines(dat$exact_time2,
         dat$Sub_metering_3,
         type="l",
         col = "blue")
    legend(x = "topright",
           legend = c("Sub_metering_1","Sub_metering_2","Sub_metering_3"),
           lty = 1,
           lwd = 2.5,
           col = c("black","red","blue"))
    
    plot(dat$exact_time2,
         dat$Global_reactive_power,
         type="l",
         xlab="datetime")
#dev.off()
```









