---
title: "Coursera R programming week2 notes2"
output: html_notebook
---
2021/06/19 SAT
```{r}
y <-10
f <- function(x){
    y <- 2
    y^2 + g(x)
}
g <- function(x) {
    x*y
}
f(3)
```

This shows the difference between Lexical Scoping and Dynamic Scopping.

```{r}

```

Consequences of Lexical Scoping
1) In R, all objects must be stored in memory.
2) All functions must carry a pointer to their respective defining environments, which could be anywhere.
3) In S-PLUS, free variables are always looked up in the global workspace, so everything can be stored on the disk because the "defining environment" of all functions is the same.

Maximizing a Normal Likelihood
```{r}
make.NegLogLik <- function(data, fixed = c(FALSE, FALSE)){
        params <- fixed
        function(p){
              params[!fixed] <- p
              mu <- params[1]
              sigma <- params[2]
              a <- -0.5*length(data)*log(2*pi*sigma^2)
              b <- -0.5*sum((data-mu)^2 / (sigma^2))
              -(a+b)
        }
}
set.seed(1); normals <- rnorm(100, 1, 2)
nLL <- make.NegLogLik(normals)
View(nLL)
ls(environment(nLL))
```
看不懂，真不知道在讲啥 TAT
mark 一下网址： https://www.coursera.org/learn/r-programming/lecture/Jm1s1/scoping-rules-optimization-example-optional



Coding Standards
1) Always use text files/ text editor
2) Indenting is IMPORTANT -> imporves readability
    Fixing line length(80 columns) prevents lots of nesting and vering long functions
    Suggested: Indents of 4 spaces at minimun; 8 spaces ideal

3)Limit
